A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-03 latex/main.tex
Fixup captions for resources
Closes #767
Closes #768

\begin{figure}
\centering
\includegraphics[width=\linewidth]{samples-per-day}
\caption{
Daily statistics of samples analyzed
during the ARG inference process.
(A) The number of samples
processed from the input sequence alignments,
exactly matched to a node in the current ARG, and
added to the ARG
all peak in December, 2022
and subsequently around February, 2022.
(B) The fraction of exactly matched samples and
the fraction of samples added to the ARG
mirror each other.
Around the peak of sample volume,
the fraction of exactly matched samples
is relatively high (above 0.50).
As expected, this fraction later decreases
when sampling effort decreases.
(C) The mean HMM cost per sample is relatively high
at the beginning as the ARG had not accumulated
enough genetic diversity yet.
(D) Proportion of samples classified
by Scorpio designation.
These proportions reflect waves of infections
driven by the emergence of Alpha, Delta, and Omicron.
}\label{fig:samples_per_day}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{inference-resources}
\caption{
Usage of computational resources
during the ARG inference process.
(A) The amount of time to process a daily batch of samples
peaks when the sampling effort is the highest.
(B) Mean time to process a sample remained low throughout,
except towards the very end when there were few exact matches.
The HMM cost was moderate initially,
then noticeably decreased when sampling effort is the highest
before increasing again towards the end.
(C) Max RAM usage also peaks around the time
when sampling effort is the highest.
}
\label{fig:inference_resources}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{samples-per-day}
\caption{
Daily statistics of samples analyzed
during the ARG inference process.
(A) The number of samples
processed from the input sequence alignments,
exactly matched to a node in the current ARG, and
added to the ARG per day.
(B) The fraction of exactly matched samples and
the fraction of samples added to the ARG
mirror each other.
The fraction of exact matches is a function of 
both sampling depth and composition of the global population.
(C) The mean HMM cost per sample is a useful metric.
(D) Proportion of samples classified by (simplified) Scorpio designation.
}\label{fig:samples_per_day}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{inference-resources}
\caption{
Computational resources used during the ARG inference process.
(A) The amount of time to process a daily batch of samples
and the number of samples processed per day.
(B) Mean time to process a sample is less than 5s except
when the number of samples is small. 
(C) RAM usage is the most difficult resource to manage, and depends
on the sample composition. The sharp drop in 2022-01 corresponds to the 
sweep in which Omicron BA.1 replaced Delta and there was very little sample
diversity. The drop in RAM usage around 2022-02 corresponds to a change
in configuration where we reduced the number of HMM threads from 128 to 80
to better fit into available memory. 
}
\label{fig:inference_resources}
\end{figure}
